Project Proposal Machine Learning

### 2012-09-16 ProjectProposal/Project.tex
Changed planing table.

@@

\paragraph{Student member names \& number:}

Joachim Daiber: 2397331\\
Carmen Klaussner: 2401541\\

@@

\paragraph{Methods:}
We believe that Structured Prediction provides a flexible and efficient model for Named Entity Recognition. 
The learning algorithm Structured Perceptron with Averaging \cite{Collins:2002:DTM:1118693.1118694}.

@@

\paragraph{Planning:}
17-23 Sep.: Data Preparation/Literature Review

24-30 Sep.: Implementation of Learning Algorithm

1-7 Okt.: Implementation of Decoding

8-14 Okt.: Improvement of Features

15-21 Okt.: Evaluation

22-28 Okt.: Paper

29-4 Nov.: Paper

>>>>

\section*{Project Proposal}

@@

\paragraph{Student member names \& number:}\\
Joachim Daiber: 2397331\\
Carmen Klaussner: 2401541\\

@@

\paragraph{Methods:}
We believe that Structured Prediction provides a flexible and efficient model for Named Entity Recognition. 
The learning algorithm is the Structured Perceptron with Averaging \cite{Collins:2002:DTM:1118693.1118694}.

@@

\section*{Planning}

\begin{table}[h!]
\begin{tabular}{l l}
17-23 Sep. & Data Preparation/Literature Review \\
24-30 Sep. & Implementation of Learning Algorithm\\
1-7 Oct.   & Implementation of Decoding\\
8-14 Oct.  & Improvement of Features\\
15-21 Oct. & Evaluation \\
22-28 Oct. & Paper \\
29-4 Nov.  & Paper\\
\end{tabular}
\end{table}
